Verifying Demonstrations

### 2018-08-22 paper/adversary-model.tex
Updates adversary figures: makes adversaries red

\begin{definition}[Base witness adversary]\label{base-witness-adversary}
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{W,P}(W)\).
  The witness later communicates with \(S\), where \(S\) only learns 
  \(f(d_{W,P}(W))\), for some function \(f\), and the time it happened, 
  \(t_{W,S}\).
  The adversary controls \(P\) and \(S\).
\end{definition}

\Cref{base-witness-adversary} is the analogous to 
\cref{base-protester-adversary}.
It is illustrated in \cref{fig:witness-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-witness-adversary.tikz}
  \caption{\label{fig:witness-adversary}%
    An overview of the base witness adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(W)\), and the 
    time it happened, \(t_{P,W}\).
    The witness submit some function of the protocol data \(f(d_{P,W}(W))\) to 
    the storage \(S\), who learns only that and the time it happened, 
    \(t_{P,S}\).
    Both the protester \(P\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

>>>>

\begin{definition}[Base witness adversary]\label{base-witness-adversary}
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{W,P}(W)\) and the time it took place, 
  \(t_{P,W}\).
  The witness later communicates with \(S\), where \(S\) only learns 
  \(f(d_{W,P}(W))\), for some function \(f\), and the time it happened, 
  \(t_{W,S}\).
  The adversary controls \(S\).
\end{definition}

\Cref{base-witness-adversary} is the analogous to 
\cref{base-protester-adversary}.
The rationale is the same as for \cref{base-protester-adversary}, the witness 
\(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
\Cref{fig:witness-adversary} illustrates the roles and relations.

\begin{figure}
  \centering
  \includegraphics{base-witness-adversary.tikz}
  \caption{\label{fig:witness-adversary}%
    An overview of the base witness adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(W)\), and the 
    time it happened, \(t_{P,W}\).
    The witness submit some function of the protocol data \(f(d_{P,W}(W))\) to 
    the storage \(S\), who learns only that and the time it happened, 
    \(t_{W,S}\).
    Both the protester \(P\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}
